%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\color{blue}Infrastructure Engineer}{Remote}
      {\it{}\underline{Reveal Group}}{Jan 2023 - Current}
      \resumeItemListStart
      \resumeItem{Serve as an Infrastructure SME, guiding clients to implement solutions on their environments}
      \resumeItem{Manage, implement, and implement Mid-to-Large IT environments}
      \resumeItem{Serve as an SME for RPA products including Blue Prism \& Automation Anywhere}
      \resumeItem{Train and share knowledge with internal staff with Microsoft and Red Hat products}
      \resumeItem{Install and launch new platforms designed by the delivery team}
      \resumeItem{Provide hands-on expertise with networking, automation, and security at the highest levels to ensure compliance with clients' standards \& best practice}
    \resumeItemListEnd
    \resumeSubheading
    {\color{blue}Systems Administrator}{Charlotte, NC}
    {\it{}\underline{WasteQuip LLC}}{Jan 2022 - Dec 2022}
      \resumeItemListStart
%       Design & implement IT Infrastructure projects in 4 key areas: Networking, Virtualization, Automation, and Cloud Computing
\resumeItem{Support 2500 users and provision IT assets (IP Phones, Computers, Software stack)}
\resumeItem{Level 3 Incident management (Analysis and resolution). Reading, analyzing and resolving log and user created incidents.}
\resumeItem{Create and maintain Azure Cloud Infrastructure (Creating Enterprise Applications, Adding new Policies in Endpoint, addressing security alerts on defender and onboard servers to Sentinel}
\resumeItem{Install, update, and maintain Fortinet, Cisco, and Sophos network equipment }
\resumeItem{Install, update, and maintain ESXi server using vSphere and its appliance.}
\resumeItem{Train Support staff and address escalated incidents.}
\resumeItem{Deploy and create Ansible Playbooks and ensure APIs are implemented and connected.}
\resumeItem{Endpoint Administration and policy management for 2500 users and implementing Autopilot onboarding and offboarding.}
\resumeItem{Server management and automation PowerShell scripting to query, update, and manage servers with ActiveDirectory}
\resumeItem{SCCM on-premises centralized management and deployment.}
      \resumeItemListEnd

    \resumeSubheading
      {\color{blue}IT Consultant and System Administrator}{Charlotte, NC}
      {\it{}\underline{CGNET Services International}}{Jan 2020 - Dec 2021}
      \resumeItemListStart
\resumeItem{      Provide day-to-day technical support for desktop computers, mobile phones, laptops, tablets, audiovisual systems, printers, and telephony systems via telephone, email or in person.}
     \resumeItem{Triage, investigate and resolve issues with IT systems within the office and manage escalations as required to 3rd tier teams.}
     \resumeItem{Create desktop and laptop imaging.}
     \resumeItem{Work as a project resource as required to deploy new systems, upgrades, or technologies within the office, which may include  personal technology and IT infrastructure.}
            \resumeItemListEnd

    \resumeSubheading
      {\color{blue}Teacher Assistant (Computer Infrastructure)}{Charlotte, NC}
      {\it{}\underline{University Of North Carolina at Charlotte}}{January 2016 - April 2016}
      \resumeItemListStart
     \resumeItem{Provide technical support for students in the ITIS 2110/3110 Computer Infrastructure course}
     \resumeItem{Help students with their computer problems and assist them with their computer issues}
     \resumeItem{Explain the course concepts and provide assistance to students in the course}
     \resumeItem{Maintain Hardware equipment and software for the course (i.e. Switches, Servers, Firewalls, Routers)}
            \resumeItemListEnd

    \resumeSubheading
      {\color{blue}Cellular Tech LLC}{Charlotte, NC}
      {Mobile \& Computer Technician}{January 2011 - February 2017} 

      \resumeItemListStart
      \resumeItem{Analyze Software/Hardware Problems and suggest solutions to address the problems}
      \resumeItem{Handle Sensitive Personal Information and safeguard computers and cell phone from future intrusion}
      \resumeItem{Install and maintain software and hardware}
      \resumeItem{Install and Maintain Operating system on Symbian, Windows, Linux, IOS Apple, and Android OS}
      \resumeItem{Public-Key Authentication Through SFTP, SSH and TLS}
            \resumeItemListEnd

  \resumeSubHeadingListEnd
% \vspace{-20pt}